
%there are four versions, one for each tute and then one suplementary. 
%the ifthen package is used to hide the different versions, and to include 
%or hide solutions. 

\documentclass[12pt]{amsart}
\usepackage{a4wide,bm,graphicx,caption,subcaption}
\captionsetup[subfigure]{labelfont=rm}
\usepackage{enumitem,ifthen}

%\newcommand{\quizVersion}{4} %set to 1, 2, 3, or 4 depending on the tutorial time

\usepackage{comment}
%\specialcomment{solution}{\textbf{Solution}\quad}{}
%\newboolean{iflecturer}
%\setboolean{iflecturer}{false}
%
%\ifthenelse{\boolean{iflecturer}}{}{\excludecomment{solution}}

\pagenumbering{gobble}

\begin{document}
%-----------------------title section
\begin{center}
{\Large Numeracy Scale}\\
\vspace{1cm}
Don't worry, it's not for a grade.
But there is a prize for the best score!
\vspace{1cm}
%You must show all your work to earn full marks.
%This can include algebraic formulas, numerical/graphical techniques, and named theorems from lectures.
%If you use a calculuator for a decimal approximation, include the formula you are evaluating.
%
%\vspace{1cm}

\begin{tabular}{@{}ll}
Time estimate:   &        {\rm \bf FIFTEEN} ($15$) minutes\\
No. of questions: &  {\rm\bf SEVEN} ($7$)\\
Total marks: & {\rm \bf SEVEN} ($7$)\\
There are: & {\rm \bf TWO} ($2$) pages\\
\end{tabular}

\vspace{1cm}

\end{center}

\begin{enumerate}

\item (1 mark) Imagine that we have a fair, 6-sided die (for example, from a board game or a casino).
Imagine we now roll it 1000 times.
Out of 1000 rolls, how many times do you think the die would come up even (numbers 2, 4, or 6)?

\vspace{2cm}

\item (1 mark) In the Cat Scratch Lottery, the chances of winning a \$10.00 prize is 1\%.
What is your best guess about how many people would win a \$10.00 prize if 1000 people each buy a single ticket to Cat Scratch?

\vspace{2cm}

\item (1 mark) In the Acme Publishing Sweepstakes, the chance of winning a car is 1 in 1000.
What percentage of tickets to the Acme Publishing Sweepstakes win a car?

\vspace{2cm}

\item (1 mark) Which of the following numbers represents the biggest risk of getting a disease?

\begin{itemize}
	\item 1 in 100
	\item 1 in 1000
	\item 1 in 10
\end{itemize}

\vspace{2cm}

\item (1 mark) Which of the following numbers represents the biggest risk of getting a disease?
\begin{itemize}
	\item 1\%
	\item 10\%
	\item 5\%
\end{itemize}

\vspace{2cm}

\item (1 mark) If person A's risk of getting a disease is 1\% over 10 years, and person B's risk is double that of A's, what is B's risk?

\vspace{2cm}

\item (1 mark) If person A's risk of getting a disease is 1 in 100 over 10 years, and person B's risk is double that of A's, what is B's risk?

\end{enumerate}

\vspace{2cm}

Out of these seven questions, how many do you think you got right?

\end{document}
